### 2022-08-31 input/conclusion.tex
meow
toward camera ready

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised to mitigate as much as
possible traffic between \processes.  In this paper, we addressed the
challenge of content indexing as a dynamic logical partitioning
problem where partitions grow and shrink to reflect content locations,
and infrastructure changes.  Using an efficient communication
primitive called scoped broadcast, each \process composing the
infrastructure eventually knows the \process hosting the closest replica
of a specific content.  The challenge resides in handling concurrent
operations that may impair the propagation of messages, and in turn,
lead to inconsistent partitioning.
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Simulations confirmed that
\processes quickly reach consistent partitioning together while the
generated traffic remains locked down to partitions.  We also 
discussed an improvement further containing the traffic inside relevant
autonomous systems.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

%% As future work, we plan to leverage the hierarchical properties of
%% interconnected autonomous systems to further limit the propagation of
%% indexes within interested systems only. We expect that such an
%% improvement would greatly benefit the autonomous systems, and
%% particularly those hosting a large number of contents.

%% Systems hosting a large number of contents would greatly benefit from
%% this improvement.

%% As future work, we plan to enable lazy retrieval of partitions when a
%% large number of contents is involved. Indeed, using \NAME, every
%% \process partakes in the propagation of all indexes which raises
%% scalability issues. We would like to leverage the hierarchical
%% properties of
%% % interconnected
%% autonomous systems to limit the
%% propagation of such indexes only to interested systems.

%
%% As ongoing and future work, we are currently studying how it might be
%% possible to limit the scope of a partition to one autonomous system at
%% most. Indeed, the gain of propagating changes to \processes belonging to
%% another autonomous system might be negligible as the latency penalty
%% is mainly due to inter autonomous systems' links (\eg trans-continental
%% links).  Exactly, we are investigating how such a change can be
%% formalized and its impact on the current protocol.
%
%autonomous systems. Indeed, \processes could leverage the hierarchical
%properties of the Internet topology~\cite{nur2018geography} to avoid
%flooding the whole systems with control information about all
%partitions.
%\TODO{should we highlight this at the end of the experiment}
%

As future work, we plan to evaluate our proposal within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem (IPFS)~\cite{ipfs}. This would
assess the relevance of \NAME in real systems subject to high
dynamicity, and compare it against its current DHT-based indexing
system that does not include distance in its operation. More
generally, we claim that \NAME and its extension can constitute novel
building blocks for geo-distributed services.  For instance, \NAME
could complement content delivery
infrastructures~\cite{triukose2011measuring} by efficiently sharing
between \processes attached to the same CDN server the locations of
web objects that have already been downloaded. This would further
improve the containment of web traffic in our networks, and in turns,
reduce the overall traffic footprint.

%% Such an integration would enable us to to perform additional
%% experiments and observe the gain with respect to the DHT-based
%% approach that is currently used.

%% In addition to this action, it would make sense to evaluate
%% the use of \NAME within a concrete storage systems, such as
%% \underline{I}nter\underline{P}lanetary \underline{F}ile
%% \underline{S}ystem (IPFS)~\cite{henningsen2020mapping}.  Such an
%% integration would enable us to to perform additional experiments and
%% observe the gain with respect to the DHT-based approach that is
%% currently used.

%
%% More generally, it can be used in other services in order to share information while mitigating the traffic.
%% MWhile we use the distance to the closest copy in this paper, It is
%% notewothy that other scopes can be envisioned according to the
%% use-cases.  For instance, the location of a city in order to broadcast
%% message to all nodes in the city.  This requires nodes to store and
%% maintain their city location in their local state. Nodes stop
%% delivering and forwarding their received messages when they come from
%% a different city. Such a predicate can be complexified in order to
%% broadcast messages to all nodes in the city plus neighboring
%% cities. This requires nodes to overload forwarded messages the first
%% time they reach another city. The predicate checks if messages already
%% reached two distinct cities before delivery.  The predicate can even
%% be piggypack within the message and so be different for each
%% message.\TODO{Complete the use-cases}

>>>>

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised to mitigate as much as
possible traffic between \processes.  In this paper, we addressed the
challenge of content indexing as a dynamic logical partitioning
problem where partitions grow and shrink to reflect content locations,
and infrastructure changes.  Using an efficient communication
primitive called scoped broadcast, each \process composing the
infrastructure eventually knows the \process hosting the closest replica
of a specific content.  The challenge resides in handling concurrent
operations that may impair the propagation of messages, and in turn,
lead to inconsistent partitioning.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME for \underline{A}daptive
\underline{S}coped broad\underline{cast}.  Simulations confirmed that
\processes quickly reach consistent partitioning together while the
generated traffic remains locked down to partitions.

As future work, we plan to leverage the hierarchical properties of
interconnected autonomous systems~\cite{nur2018geography} to further
limit the propagation of indexes within interested systems only.  We
expect that such an improvement would greatly benefit the autonomous
systems, and particularly those hosting a large number of contents.
Indeed, \NAME ensures that every \process eventually acknowledges its
closest content replica. This feature unfortunately becomes an issue
when each \process is only interested by a small portion of
content.

We also plan to evaluate our proposal within a concrete storage system
such as \underline{I}nter\underline{P}lanetary \underline{F}ile
\underline{S}ystem (IPFS)~\cite{ipfs}. This would assess the relevance
of \NAME in real systems subject to high dynamics, and compare it
against its current DHT-based indexing system that does not include
distance in its operation. More generally, we claim that \NAME and its
extension can constitute novel building blocks for geo-distributed
services.  For instance, \NAME could complement content delivery
infrastructures~\cite{triukose2011measuring} by efficiently sharing
between \processes attached to the same CDN server the locations of
web objects that have already been downloaded. This would further
improve the containment of web traffic in our networks, and in turns,
reduce the overall traffic footprint.
%
%% More generally, it can be used in other services in order to share information while mitigating the traffic.
%% MWhile we use the distance to the closest copy in this paper, It is
%% notewothy that other scopes can be envisioned according to the
%% use-cases.  For instance, the location of a city in order to broadcast
%% message to all nodes in the city.  This requires nodes to store and
%% maintain their city location in their local state. Nodes stop
%% delivering and forwarding their received messages when they come from
%% a different city. Such a predicate can be complexified in order to
%% broadcast messages to all nodes in the city plus neighboring
%% cities. This requires nodes to overload forwarded messages the first
%% time they reach another city. The predicate checks if messages already
%% reached two distinct cities before delivery.  The predicate can even
%% be piggypack within the message and so be different for each
%% message.\TODO{Complete the use-cases}

### 2022-08-31 input/proposal.tex
toward camera ready

To provide dynamic logical partitioning using scoped broadcast, all
live \processes must collaborate to disseminate messages that notify
new or removed sources to all and only interested \processes. This
section reviews step-by-step the properties that allow \processes to
converge to the desired state together. It first defines scoped
broadcast, then uses it to guarantee consistent partitioning when a
\process can only become a new source in the system. It highlights the
issue when a \process can also remove its status of source. It shows
that using local knowledge and scoped broadcast, \processes can still
reach dynamic consistent partitioning when they are able to detect
possible blocking conditions in the dissemination of required
notifications, even in dynamic networks where nodes join, leave, or
crash. % at any time.
For convenience, Table~\ref{table:notations}
summarizes the notations used throughout the paper.

@@

A naive attempt at implementing DCP resembles echoes in acoustics: a
sound propagates in the air before crashing into surrounding walls to
finally come back altered. Following the principles of scoped
broadcast as stated in Definition~\ref{def:scoped}, a \process $x$
that receives a staleness notification $\delta_s$ forwards it only if
the latter targets its current partition $\alpha_s$. The staleness
notifications propagate through the network as long as they remain in
the deleted partition. When they reach the bordering \processes of the
deleted partition, it creates an echo of bordering partitions that
will go backward to fill the gap left open by removals using
forwarding of best (FB) as stated by Theorem~\ref{theo:fb}.

@@

\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos]
  In addition to FB, a \process $x$ that receives but does not deliver
  a staleness notification $\delta_{s}$ replies by --~or echoes~-- its
  best up-to-date delivered message: $(\last D_x = \alpha_{s'}^d
  \wedge \delta_{s'} \not\in D_x \wedge d_x(\alpha_{s'}^d)\rightarrow
  r_{xy}(\delta_{s})) \implies r_{xy}(\delta_{s}) \rightarrow
  s_{xy}(\alpha_{s'}^d\oplus^{w_{xy}})$.
\end{definition}

>>>>

To provide dynamic logical partitioning using scoped broadcast, all
live \processes must collaborate to disseminate messages that notify
new or removed sources to all and only interested \processes. This
section reviews step-by-step the properties that allow \processes to
converge to the desired state together. It first defines scoped
broadcast, then uses it to guarantee consistent partitioning when a
\process can only become a new source in the system. It highlights the
issue when a \process can also remove its status of source. It shows
that using local knowledge and scoped broadcast, \processes can still
reach dynamic consistent partitioning when they are able to detect
possible blocking conditions in the dissemination of required
notifications, even in dynamic networks where nodes join, leave, or
crash at any time.
For convenience, Table~\ref{table:notations}
summarizes the notations used throughout the paper.

@@

A naive attempt at implementing DCP resembles echoes in acoustics: a
sound propagates in the air before crashing into surrounding walls to
finally come back altered. Following the principles of scoped
broadcast as stated in Definition~\ref{def:scoped}, a \process $x$
that receives a staleness notification $\delta_s$ forwards it only if
the latter targets its current partition $\alpha_s$. These messages
propagate as long as they remain in the deleted partition. When they
reach the bordering \processes of the deleted partition, it creates an
echo of bordering partitions that will go backward to fill the gap
left open by removals using forwarding of best (FB) as stated by
Theorem~\ref{theo:fb}.

@@

\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos]
  In addition to FB, a \process $x$ that receives but does not deliver
  a staleness notification $\delta_{s}$ replies by --~or echoes~-- its
  best up-to-date delivered message:\\$(\last D_x = \alpha_{s'}^d
  \wedge \delta_{s'} \not\in D_x \wedge d_x(\alpha_{s'}^d)\rightarrow
  r_{xy}(\delta_{s})) \implies r_{xy}(\delta_{s}) \rightarrow
  s_{xy}(\alpha_{s'}^d\oplus^{w_{xy}})$.
\end{definition}
